---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# fics 

Contains a function (`fics`) for creating conspiracy items using the Flexible Inventory of Conspiracy Suspicions (FICS; Wood, 2017).

## Installation

The development version of `fics` can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("camkay/fics")
```

## Descriptions and Examples

```{r setup, include = FALSE}
# load panoply
library(fics)

# suppress scientific notation
options(scipen = 999)
```

### column_find

`fics` creates items assessing the belief in a conspiracy about a given topic. The items are created using the Flexible Inventory of Conspiracy Suspicions (FICS) template (Wood, 2017).

```{r fics}
fics("Canada")

```

## References

Wood, M. J. (2017). Conspiracy suspicions as a proxy for beliefs in conspiracy theories: Implications for theory and measurement. *British Journal of Psychology, 108*(3), 507–527. https://doi.org/10.1111/bjop.12231